Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-02 paper/manuscript.Rmd
adjust to use text ref, fig1

![**Figure 1**: Image of swimming unmarked adult male caribou (*Rangifer tarandus*) from Western to Eastern Indian Island taken on 30 May 2017.](../graphics/IMG_1562.JPG)

>>>>

(ref:fig1) Image of swimming unmarked adult male caribou (*Rangifer tarandus*) from Western to Eastern Indian Island taken on 30 May 2017.

```{r, fig.cap = '(ref:fig1)'}
knitr::include_graphics('../graphics/IMG_1562.JPG')
```
